|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
modify plot for different heter shape

# Generate data for a = -1
ori_dat <- heter_model(a = -1, 
                       x = {
                         raw_x <- rand_uniform(-1, 1);
                         closed_form(~stand_dist(raw_x))
                         }, 
                       b = 128)$gen(300)

# Plot data for a = -1
hp1 <- VI_MODEL$plot(ori_dat) +
  ggtitle(quote("A. a = -1: Left-triangle")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Plot data for a = 0
hp2 <- heter_model(a = 0, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 128)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("B. a = 0: Butterfly")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Plot data for a = 1
hp3 <- heter_model(a = 1, 
                   x = {
                     raw_x <- rand_uniform(-1, 1); 
                     closed_form(~stand_dist(raw_x))
                     }, 
                   b = 128)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote("C. a = 1: Right-triangle")) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(hp1, hp2, hp3, ncol = 3)
```

>>>>

a_labels <- c("Left-triangle", "Butterfly", "Right-triangle")

# Generate data for a = -1
dat_a_n1 <- heter_model(a = -1, 
                        x = {
                          raw_x <- rand_uniform(-1, 1);
                          closed_form(~stand_dist(raw_x))
                          },
                        b = 128)$gen(300) %>%
  mutate(a = a_labels[1])

# Generate data for other a
map(c(0, 1), function(a) {
  heter_model(a = a,
              x = {
                raw_x <- rand_uniform(-1, 1); 
                closed_form(~stand_dist(raw_x))
                }, 
              b = 128)$
    gen(300, computed = select(dat_a_n1, x, e)) %>%
    mutate(a = a_labels[a + 2])
}) %>%

  # Combined with data for a = -1
  bind_rows(dat_a_n1) %>%
  mutate(a = factor(a, levels = a_labels)) %>%
  VI_MODEL$plot() +
  facet_wrap(~a, scales = "free", ncol = 3) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```
